---
title: "Graphik_für_Latex"
author: "Linus Benetz"
date: "2026-08-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r general, message=FALSE, results='hide'}

rm(list = ls())

library("rio")
library("here")
library("readxl")
library("tidyr")
library("dplyr")
library("ggplot2")
library("viridis")
library("janitor")
library("purrr") # für map Befehl
library("tidyverse")
library("ggpmisc")
library("patchwork")
library("ggtext")
library("scales") # maskiert col_factor readr; discard von purrr; viridis_pal von viridis 
#-> muss wenn ich die aus den anderen Pakten haben will direkt ansprechen mit viridis::vidis_pal

source(here::here("04_visual/R_Skripte", "Latex_Visualisierung_Funktionen.r"))

here()


```

# Developement of $CH_4$ over all Sectors

### DEU

Data preparing.

```{r DEU_Import,  results='hide'}

DEU_CH4_all_sectors <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_DEU_90_24.csv")
)

DEU_wo_Cat_enterfe <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_DEU.csv"))
summary(DEU_wo_Cat_enterfe)

DEU_CH4_all_sectors_wo_Cat_enterfe <- DEU_CH4_all_sectors |> 
  mutate(total_CH4_wo_Cat_EnterFe_in_kt = DEU_wo_Cat_enterfe$total_CH4_wo_Cat_EnterFe_in_kt) |> 
  mutate(
    share_total_of_Cat_enterfe_in_procent = 100 - (total_CH4_wo_Cat_EnterFe_in_kt/Total_CH4_in_kt * 100),
    share_agric_of_Cat_enterfe_in_procent = (DEU_wo_Cat_enterfe$Cat_EnterFer_pred_in_kt/ Agriculture_in_kt *100)
  )

summary(DEU_CH4_all_sectors_wo_Cat_enterfe)

export(DEU_CH4_all_sectors_wo_Cat_enterfe,
       file = here("03_Analyses/tables/ExtraPol_data", "Emission_all_Sector_plus_wo_Cat_Enterfe_DEU.csv"))

DEU_CH4_Agric_Sect <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_DEU_90_24.csv")
)

summary(DEU_CH4_Agric_Sect)

```
### NZL

```{r NZL-import, results='hide'}

NZL_CH4_all_sectors <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_NZL_90_24.csv")
)

summary(NZL_CH4_all_sectors)


NZL_wo_Cat_enterfe <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_NZL.csv"))
summary(NZL_wo_Cat_enterfe)

NZL_CH4_all_sectors_wo_Cat_enterfe <- NZL_CH4_all_sectors |> 
  mutate(total_CH4_wo_Cat_EnterFe_in_kt = NZL_wo_Cat_enterfe$total_CH4_wo_Cat_EnterFe_in_kt) |> 
  mutate(
    share_total_of_Cat_enterfe_in_procent = 100 - (total_CH4_wo_Cat_EnterFe_in_kt/Total_CH4_in_kt * 100),
    share_agric_of_Cat_enterfe_in_procent = (NZL_wo_Cat_enterfe$Cat_EnterFer_pred_in_kt/Agriculture_in_kt * 100)
  )

summary(NZL_CH4_all_sectors_wo_Cat_enterfe)

export(NZL_CH4_all_sectors_wo_Cat_enterfe,
       file = here("03_Analyses/tables/ExtraPol_data", "Emission_all_Sector_plus_wo_Cat_Enterfe_NZL.csv"))



NZL_CH4_AGRICULTURE_Sector <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_NZL_90_24.csv")
)

summary(NZL_CH4_AGRICULTURE_Sector)
```

### USA

```{r USA-import, results='hide'}

USA_CH4_all_sectors <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_USA_90_22.csv")
)

summary(USA_CH4_all_sectors)

USA_wo_Cat_enterfe <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_USA.csv"))
summary(USA_wo_Cat_enterfe)

USA_CH4_all_sectors_wo_Cat_enterfe <- USA_CH4_all_sectors |> 
  mutate(total_CH4_wo_Cat_EnterFe_in_kt = USA_wo_Cat_enterfe$total_CH4_wo_Cat_EnterFe_in_kt) |> 
  mutate(
    share_total_of_Cat_enterfe_in_procent = 100 - (total_CH4_wo_Cat_EnterFe_in_kt/Total_CH4_in_kt * 100),
    share_agric_of_Cat_enterfe_in_procent = (USA_wo_Cat_enterfe$Cat_EnterFer_pred_in_kt/Agriculture_in_kt * 100)
  )

summary(USA_CH4_all_sectors_wo_Cat_enterfe)

export(USA_CH4_all_sectors_wo_Cat_enterfe,
       file = here("03_Analyses/tables/ExtraPol_data", "Emission_all_Sector_plus_wo_Cat_Enterfe_USA.csv"))

USA_CH4_AGRICULTURE_Sector <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_USA_90_22.csv")
)

summary(USA_CH4_AGRICULTURE_Sector)
```

## Plotting time series total CH4

```{r}
Deu_all_sec <- All_sectors_CC_specific_function(df = DEU_CH4_all_sectors_wo_Cat_enterfe, lm = 5.5, br_lm = 6, 
                                                bei = 1, CC = "DEU", pt_size = 1)

Deu_all_sec

Nzl_all_sec <- All_sectors_CC_specific_function(df = NZL_CH4_all_sectors_wo_Cat_enterfe, lm = 5.5, br_lm = 6, 
                                                bei = 1, CC = "NZL", pt_size = 1)

Nzl_all_sec

USA_all_sec <- All_sectors_CC_specific_function(df = USA_CH4_all_sectors_wo_Cat_enterfe, lm = 35, br_lm = 40, 
                                                bei = 5, CC = "USA", pt_size = 1)

USA_all_sec

all_CC_all_sectors <- (Deu_all_sec + Nzl_all_sec + USA_all_sec) + guide_area() +
  plot_layout(ncol = 2, guides = "collect")
all_CC_all_sectors

ggsave(plot = all_CC_all_sectors,
       filename = here("../Text_Production/figures/Results/GEO", "All_CC_all_sectors.pdf"))

```

## Sharechange of cattle EnterFe on total CH4 and Agriculture

```{r}
DEU_share <- Share_change_plot_function(df = DEU_CH4_all_sectors_wo_Cat_enterfe, lm = 80, br_lm = 100, bei = 20, CC = "DEU")

DEU_share

NZL_share <- Share_change_plot_function(df = NZL_CH4_all_sectors_wo_Cat_enterfe, lm = 80, br_lm = 100, bei = 20, CC = "NZL")

NZL_share

USA_share <- Share_change_plot_function(df = USA_CH4_all_sectors_wo_Cat_enterfe, lm = 80, br_lm = 100, bei = 20, CC = "USA")

USA_share


Share_all_CC <- (DEU_share + NZL_share + USA_share) + guide_area() +
  plot_layout(ncol = 2, guides = "collect")

Share_all_CC

ggsave(plot = Share_all_CC,
       filename = here("../Text_Production/figures/Results/GEO", "Share_of_cat_EnterFe_all_CC.pdf"))

```
# Per country: important Indicators for calculation of methane

First, data import.

```{r Data_Import, message=FALSE, results='hide'}

CH4_emis_Ym_DE_DEU_1990_2024 <- read.csv(
  file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_DEU_1990_2024.csv"))

CH4_emis_Ym_DE_NZL_1990_2024 <- read.csv(
  file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_NZL_1990_2024.csv"))

CH4_emis_Ym_DE_USA_1990_2022 <- read.csv(
  file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_USA_1990_2022.csv"))

summary(CH4_emis_Ym_DE_DEU_1990_2024)

```

### DEU

```{r}

Deu_indicator_plot <- Indicator_plot_function(df = CH4_emis_Ym_DE_DEU_1990_2024, lm = 20, br_lm = 100, bei = 5)

Deu_indicator_plot

ggsave(plot = Deu_indicator_plot,
       filename = here("../Text_Production/figures/Results/GEO", "Indicitaor_plot_DEU.pdf"))

```
### NZL

```{r}

Nzl_indicator_plot <- Indicator_plot_function(df = CH4_emis_Ym_DE_NZL_1990_2024, lm = 20, br_lm = 100, bei = 5)

Nzl_indicator_plot

ggsave(plot = Nzl_indicator_plot,
       filename = here("../Text_Production/figures/Results/GEO", "Indicitaor_plot_NZL.pdf"))
```
### USA

```{r}

USA_indicator_plot <- Indicator_plot_function(df = CH4_emis_Ym_DE_USA_1990_2022, lm = 120, br_lm = 140, bei = 40)

USA_indicator_plot

CH4_emis_Ym_DE_USA_1990_2022$Ch4_emission_org_in_kt

ggsave(plot = USA_indicator_plot,
       filename = here("../Text_Production/figures/Results/GEO", "Indicitaor_plot_USA.pdf"))
```
# Cattle EnterFe emission time series

### All Country

```{r}

EnterFE_methane_emis_time_series_DEU <- 
  EnterFe_emission_plot_function(df = CH4_emis_Ym_DE_DEU_1990_2024, lm = 2, br_lm = 20, bei = 0.5, CC = "DEU")

EnterFE_methane_emis_time_series_DEU

EnterFE_methane_emis_time_series_NZL <- 
  EnterFe_emission_plot_function(df = CH4_emis_Ym_DE_NZL_1990_2024, lm = 2, br_lm = 20, bei = 0.5, CC = "NZL")

EnterFE_methane_emis_time_series_NZL

EnterFE_methane_emis_time_series_USA <- 
  EnterFe_emission_plot_function(df = CH4_emis_Ym_DE_USA_1990_2022, lm = 8, br_lm = 20, bei = 2, CC = "USA")

EnterFE_methane_emis_time_series_USA

EnterFe_all_CC <- EnterFE_methane_emis_time_series_DEU + EnterFE_methane_emis_time_series_NZL + EnterFE_methane_emis_time_series_USA + guide_area() + plot_layout(ncol = 2, guides = "collect")

EnterFe_all_CC

ggsave(plot = EnterFe_all_CC,
       filename = here("../Text_Production/figures/Results/GEO", "Cat_EnterFe_time_series_all_CC.pdf")
       )

```

# Boxplots for saved $CH_4$ 

Take as reference time sample 2009 to 2019, because reference figure did it to, where they calculated atmospheric growth rate for $CH_4$.

```{r}

```

