---
title: "Graphik_für_Latex"
author: "Linus Benetz"
date: "2026-08-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r general, message=FALSE, results='hide'}

rm(list = ls())


library("khroma")
library("ggsci")
library("rio")
library("RColorBrewer")
library("here")
library("readxl")
library("tidyr")
library("dplyr")
library("ggplot2")
library("viridis")
library("janitor")
library("purrr") # für map Befehl
library("tidyverse")
library("MetBrewer") 
library("ggpmisc")
library("xtable")
library("patchwork")
library("ggtext")
library("scales") # maskiert col_factor readr; discard von purrr; viridis_pal von viridis 
#-> muss wenn ich die aus den anderen Pakten haben will direkt ansprechen mit viridis::vidis_pal

source(here::here("04_visual/R_Skripte", "Latex_Visualisierung_Funktionen.r"))

here()


```

# Developement of $CH_4$ over all Sectors

### DEU

Data preparing.

```{r DEU_Import,  results='hide'}

DEU_CH4_all_sectors <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_DEU_90_24.csv")
)

DEU_wo_Cat_enterfe <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_DEU.csv"))
summary(DEU_wo_Cat_enterfe)

DEU_CH4_all_sectors_wo_Cat_enterfe <- DEU_CH4_all_sectors |> 
  mutate(total_CH4_wo_Cat_EnterFe_in_kt = DEU_wo_Cat_enterfe$total_CH4_wo_Cat_EnterFe_in_kt) |> 
  mutate(
    share_total_of_Cat_enterfe_in_procent = 100 - (total_CH4_wo_Cat_EnterFe_in_kt/Total_CH4_in_kt * 100),
    share_agric_of_Cat_enterfe_in_procent = (DEU_wo_Cat_enterfe$Cat_EnterFer_pred_in_kt/Agriculture_in_kt*100)
  )

summary(DEU_CH4_all_sectors_wo_Cat_enterfe)

export(DEU_CH4_all_sectors_wo_Cat_enterfe,
       file = here("03_Analyses/tables/ExtraPol_data", "Emission_all_Sector_plus_wo_Cat_Enterfe_DEU.csv"))

DEU_CH4_Agric_Sect <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_DEU_90_24.csv")
)

summary(DEU_CH4_Agric_Sect)

```
### NZL

```{r NZL-import, results='hide'}

NZL_CH4_all_sectors <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_NZL_90_24.csv")
)

summary(NZL_CH4_all_sectors)


NZL_wo_Cat_enterfe <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_NZL.csv"))
summary(NZL_wo_Cat_enterfe)


NZL_CH4_all_sectors_wo_Cat_enterfe <- NZL_CH4_all_sectors |> 
  mutate(total_CH4_wo_Cat_EnterFe_in_kt = NZL_wo_Cat_enterfe$total_CH4_wo_Cat_EnterFe_in_kt) |> 
  mutate(
    share_total_of_Cat_enterfe_in_procent = 100 - (total_CH4_wo_Cat_EnterFe_in_kt/Total_CH4_in_kt * 100),
    share_agric_of_Cat_enterfe_in_procent = (NZL_wo_Cat_enterfe$Cat_EnterFer_pred_in_kt/Agriculture_in_kt * 100)
  )

summary(NZL_CH4_all_sectors_wo_Cat_enterfe)

export(NZL_CH4_all_sectors_wo_Cat_enterfe,
       file = here("03_Analyses/tables/ExtraPol_data", "Emission_all_Sector_plus_wo_Cat_Enterfe_NZL.csv"))



NZL_CH4_AGRICULTURE_Sector <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_NZL_90_24.csv")
)

summary(NZL_CH4_AGRICULTURE_Sector)
```

### USA

```{r USA-import, results='hide'}

USA_CH4_all_sectors <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_USA_90_22.csv")
)

summary(USA_CH4_all_sectors)

USA_wo_Cat_enterfe <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_USA.csv"))
summary(USA_wo_Cat_enterfe)

USA_CH4_all_sectors_wo_Cat_enterfe <- USA_CH4_all_sectors |> 
  mutate(total_CH4_wo_Cat_EnterFe_in_kt = USA_wo_Cat_enterfe$total_CH4_wo_Cat_EnterFe_in_kt) |> 
  mutate(
    share_total_of_Cat_enterfe_in_procent = 100 - (total_CH4_wo_Cat_EnterFe_in_kt/Total_CH4_in_kt * 100),
    share_agric_of_Cat_enterfe_in_procent = (USA_wo_Cat_enterfe$Cat_EnterFer_pred_in_kt/Agriculture_in_kt * 100)
  )

summary(USA_CH4_all_sectors_wo_Cat_enterfe)

export(USA_CH4_all_sectors_wo_Cat_enterfe,
       file = here("03_Analyses/tables/ExtraPol_data", "Emission_all_Sector_plus_wo_Cat_Enterfe_USA.csv"))

USA_CH4_AGRICULTURE_Sector <- import(
  file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_USA_90_22.csv")
)

summary(USA_CH4_AGRICULTURE_Sector)
```

## Plotting time series total CH4

```{r}
Deu_all_sec <- All_sectors_CC_specific_function(df = DEU_CH4_all_sectors_wo_Cat_enterfe, lm = 5.5, br_lm = 6, 
                                                bei = 1, CC = "DEU", pt_size = 1)

Deu_all_sec

Nzl_all_sec <- All_sectors_CC_specific_function(df = NZL_CH4_all_sectors_wo_Cat_enterfe, lm = 5.5, br_lm = 6, 
                                                bei = 1, CC = "NZL", pt_size = 1)

Nzl_all_sec

USA_all_sec <- All_sectors_CC_specific_function(df = USA_CH4_all_sectors_wo_Cat_enterfe, lm = 35, br_lm = 40, 
                                                bei = 5, CC = "USA", pt_size = 1)

USA_all_sec

all_CC_all_sectors <- (Deu_all_sec + Nzl_all_sec + USA_all_sec) + guide_area() +
  plot_layout(ncol = 2, guides = "collect")
all_CC_all_sectors

ggsave(plot = all_CC_all_sectors,
       filename = here("../Text_Production/figures/Results/GEO", "All_CC_all_sectors.pdf"))

```

## Sharechange of cattle EnterFe on total CH4 and Agriculture

```{r}
DEU_share <- Share_change_plot_function(df = DEU_CH4_all_sectors_wo_Cat_enterfe, lm = 80, br_lm = 100, bei = 20, CC = "DEU")

DEU_share

NZL_share <- Share_change_plot_function(df = NZL_CH4_all_sectors_wo_Cat_enterfe, lm = 80, br_lm = 100, bei = 20, CC = "NZL")

NZL_share

USA_share <- Share_change_plot_function(df = USA_CH4_all_sectors_wo_Cat_enterfe, lm = 80, br_lm = 100, bei = 20, CC = "USA")

USA_share


Share_all_CC <- (DEU_share + NZL_share + USA_share) + guide_area() +
  plot_layout(ncol = 2, guides = "collect")

Share_all_CC

ggsave(plot = Share_all_CC,
       filename = here("../Text_Production/figures/Results/GEO", "Share_of_cat_EnterFe_all_CC.pdf"))

```
# Per country: important Indicators for calculation of methane

First, data import.

```{r Data_Import, message=FALSE, results='hide'}

CH4_emis_Ym_DE_DEU_1990_2024 <- read.csv(
  file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_DEU_1990_2024.csv"))

CH4_emis_Ym_DE_NZL_1990_2024 <- read.csv(
  file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_NZL_1990_2024.csv"))

CH4_emis_Ym_DE_USA_1990_2022 <- read.csv(
  file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_USA_1990_2022.csv"))

summary(CH4_emis_Ym_DE_DEU_1990_2024)

```

### DEU

```{r}

Deu_indicator_plot <- Indicator_plot_function(df = CH4_emis_Ym_DE_DEU_1990_2024, lm = 20, br_lm = 100, bei = 5)

Deu_indicator_plot

ggsave(plot = Deu_indicator_plot,
       filename = here("../Text_Production/figures/Results/GEO", "Indicitaor_plot_DEU.pdf"))

```
### NZL

```{r}

Nzl_indicator_plot <- Indicator_plot_function(df = CH4_emis_Ym_DE_NZL_1990_2024, lm = 20, br_lm = 100, bei = 5)

Nzl_indicator_plot

ggsave(plot = Nzl_indicator_plot,
       filename = here("../Text_Production/figures/Results/GEO", "Indicitaor_plot_NZL.pdf"))
```
### USA

```{r}

USA_indicator_plot <- Indicator_plot_function(df = CH4_emis_Ym_DE_USA_1990_2022, lm = 120, br_lm = 140, bei = 40)

USA_indicator_plot

CH4_emis_Ym_DE_USA_1990_2022$Ch4_emission_org_in_kt

ggsave(plot = USA_indicator_plot,
       filename = here("../Text_Production/figures/Results/GEO", "Indicitaor_plot_USA.pdf"))
```
# Cattle EnterFe emission time series

### All Country

```{r}

EnterFE_methane_emis_time_series_DEU <- 
  EnterFe_emission_plot_function(df = CH4_emis_Ym_DE_DEU_1990_2024, lm = 2, br_lm = 20, bei = 0.5, CC = "DEU")

EnterFE_methane_emis_time_series_DEU

EnterFE_methane_emis_time_series_NZL <- 
  EnterFe_emission_plot_function(df = CH4_emis_Ym_DE_NZL_1990_2024, lm = 2, br_lm = 20, bei = 0.5, CC = "NZL")

EnterFE_methane_emis_time_series_NZL

EnterFE_methane_emis_time_series_USA <- 
  EnterFe_emission_plot_function(df = CH4_emis_Ym_DE_USA_1990_2022, lm = 8, br_lm = 20, bei = 2, CC = "USA")

EnterFE_methane_emis_time_series_USA

EnterFe_all_CC <- EnterFE_methane_emis_time_series_DEU + EnterFE_methane_emis_time_series_NZL + EnterFE_methane_emis_time_series_USA + guide_area() + plot_layout(ncol = 2, guides = "collect")

EnterFe_all_CC

ggsave(plot = EnterFe_all_CC,
       filename = here("../Text_Production/figures/Results/GEO", "Cat_EnterFe_time_series_all_CC.pdf"))

```

# Boxplots for saved $CH_4$ 

Take as reference time sample 2009 to 2019, because reference figure did it to, where they calculated atmospheric growth rate for $CH_4$.

### Data preparing
For stacking the values of the several countries, first we have to process the data and collect the data in one single table
```{r}

names(CH4_emis_Ym_DE_DEU_1990_2024)

All_CC_CH4_Ym_DE_change_data <- rbind(CH4_emis_Ym_DE_DEU_1990_2024 |> 
                                        filter(Animal == "Cattle") |> 
  transmute(Year, Red_in_perc, CH4_Ym_in_kt_diff, CH4_Ym_De_in_kt_diff, CH4_Ym_and_Ym_DE_in_kt_diff) |> 
  mutate(
    Country = rep("DEU", n()), .after = Year
  ) |> 
  filter(Year %in% c(2010:2019)) |> 
  group_by(Country, Red_in_perc) |> 
  summarise(
    CH4_Ym_in_kt_diff = mean(CH4_Ym_in_kt_diff),
    CH4_Ym_De_in_kt_diff = mean(CH4_Ym_De_in_kt_diff),
    CH4_Ym_and_Ym_DE_in_kt_diff = mean(CH4_Ym_and_Ym_DE_in_kt_diff),
    .groups = "drop"
  ),
  CH4_emis_Ym_DE_NZL_1990_2024 |> 
    filter(Animal == "Cattle") |>
  transmute(Year, Red_in_perc, CH4_Ym_in_kt_diff, CH4_Ym_De_in_kt_diff, CH4_Ym_and_Ym_DE_in_kt_diff) |> 
  mutate(
    Country = rep("NZL", n()), .after = Year
  ) |> 
  filter(Year %in% c(2010:2019)) |> 
  group_by(Country, Red_in_perc) |> 
  summarise(
    CH4_Ym_in_kt_diff = mean(CH4_Ym_in_kt_diff),
    CH4_Ym_De_in_kt_diff = mean(CH4_Ym_De_in_kt_diff),
    CH4_Ym_and_Ym_DE_in_kt_diff = mean(CH4_Ym_and_Ym_DE_in_kt_diff),
    .groups = "drop"
  ),
  CH4_emis_Ym_DE_USA_1990_2022 |> 
    filter(Animal == "Cattle") |>
  transmute(Year, Red_in_perc, CH4_Ym_in_kt_diff, CH4_Ym_De_in_kt_diff, CH4_Ym_and_Ym_DE_in_kt_diff) |> 
  mutate(
    Country = rep("USA", n()), .after = Year
  ) |> 
  filter(Year %in% c(2010:2019)) |> 
  group_by(Country, Red_in_perc) |> 
  summarise(
    CH4_Ym_in_kt_diff = mean(CH4_Ym_in_kt_diff),
    CH4_Ym_De_in_kt_diff = mean(CH4_Ym_De_in_kt_diff),
    CH4_Ym_and_Ym_DE_in_kt_diff = mean(CH4_Ym_and_Ym_DE_in_kt_diff),
    .groups = "drop"
  )) |> 
   mutate(Country = factor(Country, levels = c("NZL", "DEU", "USA")),
          CH4_dif_Ym_DE_in_kt_CO2_eq_GWP_20 = CH4_Ym_De_in_kt_diff*79.7,
          CH4_dif_Ym_DE_in_kt_CO2_eq_GWP_100 = CH4_Ym_De_in_kt_diff*27)

export(All_CC_CH4_Ym_DE_change_data,
       file = here("03_Analyses/tables/Ym_and_DE_change_simple", "Saved_CH4_YM_DE_mean_2010_2019.csv"))


glimpse(All_CC_CH4_Ym_DE_change_data)
```


#### Exporting the relevatn data as a table for latex

```{r}
All_CC_CH4_Ym_DE_change_data_latex <- All_CC_CH4_Ym_DE_change_data |> 
  select(-c(CH4_Ym_and_Ym_DE_in_kt_diff, CH4_Ym_in_kt_diff)) |> 
  rename(
     "Red.-scenario" = Red_in_perc,
     "CH<sub>4</sub> [kt]" = CH4_Ym_De_in_kt_diff,
     "GWP20 [kt CO<sub>2</sub> eq.]" = CH4_dif_Ym_DE_in_kt_CO2_eq_GWP_20,
     "GWP100 [kt CO<sub>2</sub> eq.]" = CH4_dif_Ym_DE_in_kt_CO2_eq_GWP_100
  )

glimpse(All_CC_CH4_Ym_DE_change_data_latex)

All_CC_CH4_Ym_DE_change_data_latex_export_ready <- xtable(All_CC_CH4_Ym_DE_change_data_latex,
                                                          caption = "Platzhalter",
                                                          digits = 2,
                                                          label = "tab:methane_save_red_sce")


#print(All_CC_CH4_Ym_DE_change_data_latex_export_ready,
#      file = here("../Text_Production/tables/04_result", "save_methane_red_sce_all_CC_10_19.tex"),
#      booktabs = TRUE,
#      include.rownames = FALSE,
#      caption.placement = "top")

```


#### Plotting of barplot

```{r}


farben_country <-  brewer.pal(n = 3, "Set2")


Farb_zuweisung <- c(
  "DEU" = farben_country[[1]],
  "NZL" = farben_country[[2]],
  "USA" = farben_country[[3]]
  )

bar_plot_all_CC_Ym_DE <- ggplot(All_CC_CH4_Ym_DE_change_data, 
                                aes(x = Red_in_perc, y = CH4_Ym_De_in_kt_diff/1000, fill = Country)) +
  geom_col() +
  scale_y_continuous(
    expand = expansion(mult = 0.05),
    limits = c(0, 5),
    breaks = seq(0, 10, 1)
  ) +
  labs(title = "CH<sub>4</sub>",
       y = "CH<sub>4</sub> in Tg",
       x = "Emissions reduction scenarios",
       fill = "Country:") +
  scale_fill_manual(
    values = Farb_zuweisung,
    limits = c("NZL", "DEU", "USA")
  ) +
  theme_bw() +
  theme(
    plot.title = element_markdown(hjust = 0.5, face = "bold", size = 13),
      panel.grid.minor = element_line(color = "grey92", linewidth = 0.1),
      axis.title.y = element_markdown(size = 11),
      axis.title.x = element_markdown(size = 11),
      axis.text.x = element_text(size = 10),
      axis.text.y = element_text(size = 10),
      legend.text = element_markdown(size = 11, vjust = 0.5),
      legend.title = element_markdown(size = 12)
  )

GWP_20 <- ggplot(All_CC_CH4_Ym_DE_change_data, 
                                aes(x = Red_in_perc, y = CH4_dif_Ym_DE_in_kt_CO2_eq_GWP_20/1000, fill = Country)) +
  geom_col() +
  scale_y_continuous(
    expand = expansion(mult = 0.05),
    limits = c(0, 370),
    breaks = seq(0, 370, 50)
  ) +
  labs(title = "GWP20",
       y = "CH<sub>4</sub> in Tg CO<sub>2</sub> eq.",
       x = "Emissions reduction scenarios",
       fill = "Country:") +
  scale_fill_manual(
    values = Farb_zuweisung,
    limits = c("NZL", "DEU", "USA")
  ) +
  theme_bw() +
  theme(
    plot.title = element_markdown(hjust = 0.5, face = "bold", size = 13),
      panel.grid.minor = element_line(color = "grey92", linewidth = 0.1),
      axis.title.y = element_markdown(size = 11),
      axis.title.x = element_markdown(size = 11),
      axis.text.x = element_text(size = 10),
      axis.text.y = element_text(size = 10),
      legend.text = element_markdown(size = 11, vjust = 0.5),
      legend.title = element_markdown(size = 12)
  )

GWP_100 <- ggplot(All_CC_CH4_Ym_DE_change_data, 
                                aes(x = Red_in_perc, y = CH4_dif_Ym_DE_in_kt_CO2_eq_GWP_100/1000, fill = Country)) +
  geom_col() +
  scale_y_continuous(
    expand = expansion(mult = 0.05),
    limits = c(0, 370),
    breaks = seq(0, 370, 50)
  ) +
  labs(title = "GWP100",
       y = "CH<sub>4</sub> in Tg CO<sub>2</sub> eq.",
       x = "Emissions reduction scenarios",
       fill = "Country:") +
  scale_fill_manual(
    values = Farb_zuweisung,
    limits = c("NZL", "DEU", "USA")
  ) +
  theme_bw() +
  theme(
    plot.title = element_markdown(hjust = 0.5, face = "bold", size = 14),
      panel.grid.minor = element_line(color = "grey92", linewidth = 0.1),
      axis.title.y = element_markdown(size = 12),
      axis.title.x = element_markdown(size = 12),
      axis.text.x = element_text(size = 11),
      axis.text.y = element_text(size = 11),
      legend.text = element_markdown(size = 12, vjust = 0.5),
      legend.title = element_markdown(size = 13)
  )


layout <- " 
#AA#
BBCC
"

bar_plot_all <- bar_plot_all_CC_Ym_DE + GWP_20 + GWP_100 +
  plot_layout(design = layout, guides = "collect") & theme( # über das lyout bestimmt wie die plots angeordnet werden
    legend.position = "bottom",
    legend.direction = "horizontal"
  )  

bar_plot_all

ggsave(plot = bar_plot_all,
       filename = here("../Text_Production/figures/Results/GEO", "Bar_plots_CH4_save_Ym_and_DE_change_of_cattle.pdf"),
       width = 20,
       height = 17,
       units = "cm")

```

# DE change

Habs jetzt doch nicht gemacht. Falls ich es doch brauch ist die Tabelle dafür jetzt vorbereitet. Man sieht an den plots, dass prozentual DE am Anfang mehr impact hat aber bei 50 einen absoluten peak an kt CH4 hat was dadurch eingespaart wird.

### Data preparing

```{r}

CH4_emis_DE_YM_DEU_1990_2024_al_CC_2022 <- rbind( map_dfr(.x = seq(0.1,1,0.1), 
                                        CH4_emission_Ym_DE_function,
                                        CC = "DEU",
                                        YE = "2024") |> filter(Year == 2022 & Animal == "Cattle") |> 
  transmute(Red_in_perc,
            country = rep("DEU", n()),
            CH4_Ym_De_in_kt_diff, 
            CH4_Ym_and_Ym_DE_in_kt_diff,
            CH4_Ym_and_Ym_DE_in_perc = CH4_Ym_and_Ym_DE_in_kt_diff/CH4_Ym_De_in_kt_diff*100),
   map_dfr(.x = seq(0.1,1,0.1), 
                                        CH4_emission_Ym_DE_function,
                                        CC = "NZL",
                                        YE = "2024") |> filter(Year == 2022 & Animal == "Cattle") |> 
  transmute(Red_in_perc,
            country = rep("NZL", n()),
            CH4_Ym_De_in_kt_diff, 
            CH4_Ym_and_Ym_DE_in_kt_diff,
            CH4_Ym_and_Ym_DE_in_perc = CH4_Ym_and_Ym_DE_in_kt_diff/CH4_Ym_De_in_kt_diff*100),
   map_dfr(.x = seq(0.1,1,0.1), 
                                        CH4_emission_Ym_DE_function,
                                        CC = "USA",
                                        YE = "2022") |> filter(Year == 2022 & Animal == "Cattle") |> 
  transmute(Red_in_perc,
            country = rep("USA", n()),
            CH4_Ym_De_in_kt_diff, 
            CH4_Ym_and_Ym_DE_in_kt_diff,
            CH4_Ym_and_Ym_DE_in_perc = CH4_Ym_and_Ym_DE_in_kt_diff/CH4_Ym_De_in_kt_diff*100)) 

summary(CH4_emis_DE_YM_DEU_1990_2024_al_CC_2022)

ggplot(CH4_emis_DE_YM_DEU_1990_2024_al_CC_2022, aes(x = Red_in_perc, y = CH4_Ym_and_Ym_DE_in_perc, colour = country)) + 
  geom_point()

ggplot(CH4_emis_DE_YM_DEU_1990_2024_al_CC_2022, aes(x = Red_in_perc, y = CH4_Ym_and_Ym_DE_in_kt_diff, colour = country)) + 
  geom_point()


```

# Prediction with diffrent scenarios

#### DATA

```{r, results='hide'}

source(file = here("04_visual/R_Skripte/Visual_prognose_2030_Skript", "Funktion_plotting.r"))

Pred_2030_final_CH4_USA <- import(
  file = here("03_Analyses/tables/ExtraPol_data/Prediction_2030/Visual_final_Emission_table", 
              "Final_total_CH4_Calc_data_23_30_USA.csv"))

Pred_2030_final_CH4_DEU <- import(
  file = here("03_Analyses/tables/ExtraPol_data/Prediction_2030/Visual_final_Emission_table", 
              "Final_total_CH4_Calc_data_25_30_DEU.csv"))

Pred_2030_final_CH4_NZL <- import(
  file = here("03_Analyses/tables/ExtraPol_data/Prediction_2030/Visual_final_Emission_table", 
              "Final_total_CH4_Calc_data_25_30_NZL.csv"))

names(Pred_2030_final_CH4_USA)

Hist_CH4_emis_data_USA <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_USA.csv"))

Hist_CH4_emis_data_DEU <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_DEU.csv"))

Hist_CH4_emis_data_NZL <- import(file = here("03_Analyses/tables/ExtraPol_data", "Factor_table_prediction_NZL.csv"))

names(Hist_CH4_emis_data_USA)


```


#### Plotting

```{r}

Plot_total_CH4_2030_sze_10_30_50_DEU <- map(seq(10,50,20),
                                            ~ Visual_total_CH4_YB_30_function(df = Pred_2030_final_CH4_DEU, 
                                                                              hs = Hist_CH4_emis_data_DEU,
                                                                              Red = .x,
                                                                              lm = 5.2,
                                                                              br_lm = 10,
                                                                              br_by = 1,
                                                                              col_org = "total_CH4_org_calc_in_kt",
                                                                              CC = "DEU")
                                            )

Plot_total_CH4_2030_sze_10_30_50_NZL <- map(seq(10,50,20),
                                            ~ Visual_total_CH4_YB_30_function(df = Pred_2030_final_CH4_NZL, 
                                                                              hs = Hist_CH4_emis_data_NZL,
                                                                              Red = .x,
                                                                              lm = 2,
                                                                              br_lm = 10,
                                                                              br_by = 0.5,
                                                                              col_org = "total_CH4_org_calc_in_kt",
                                                                              CC = "NZL")
                                            )

Plot_total_CH4_2030_sze_10_30_50_USA <- map(seq(10,50,20),
                                            ~ Visual_total_CH4_YB_30_function(df = Pred_2030_final_CH4_USA, 
                                                                              hs = Hist_CH4_emis_data_USA,
                                                                              Red = .x,
                                                                              lm = 35,
                                                                              br_lm = 40,
                                                                              br_by = 10,
                                                                              col_org = "total_CH4_org_calc_in_kt",
                                                                              CC = "USA")
                                            )


#wrap_plots(c(Plot_total_CH4_2030_sze_10_30_50_DEU, Plot_total_CH4_2030_sze_10_30_50_NZL, Plot_total_CH4_2030_sze_10_30_50_USA), ncol = 3) + 
 # plot_layout(guides = "collect") & theme(legend.direction = "horizontal",
  #                                        legend.position = "bottom")

### alle zusammen wird zu unübersichtlich

DEU_pred_plot_final <- wrap_plots(Plot_total_CH4_2030_sze_10_30_50_DEU, ncol = 2) + guide_area() + 
  plot_layout(guides = "collect") 

ggsave(plot = DEU_pred_plot_final,
       filename = here("../Text_Production/figures/Results/GEO", "Pred_2030_total_CH4_DEU.pdf"),
       width = 27,
       height = 24,
       units = "cm")

NZL_pred_plot_final <- wrap_plots(Plot_total_CH4_2030_sze_10_30_50_NZL, ncol = 2) + guide_area() + 
  plot_layout(guides = "collect") 

ggsave(plot = NZL_pred_plot_final,
       filename = here("../Text_Production/figures/Results/GEO", "Pred_2030_total_CH4_NZL.pdf"),
       width = 27,
       height = 24,
       units = "cm")

USA_pred_plot_final <- wrap_plots(Plot_total_CH4_2030_sze_10_30_50_USA, ncol = 2) + guide_area() + 
  plot_layout(guides = "collect") 

ggsave(plot = USA_pred_plot_final,
       filename = here("../Text_Production/figures/Results/GEO", "Pred_2030_total_CH4_USA.pdf"),
       width = 27,
       height = 24,
       units = "cm")



```

