---
title: "Analyse_methane_reduction_DE_Ym_simple"
author: "Linus Benetz"
date: "2026-07-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library("here")

source(file = here("03_Analyses/Ym_und_DE_verändern_Skripte", "Function_Analyses_methane_reduction_simple.r"))
```


```{r, message=FALSE, results='hide'}
#rm(list = ls()) # enviroment säubern

#install.packages("rio")
#install.packages("janitor")

library("rio")
library("here")
library("readxl")
library("tidyr")
library("dplyr")
library("ggplot2")
library("viridis")
library("janitor")
library("purrr") # für map Befehl

here()

```

# General

In this part I calculate the reduced CH4 Emission for a working microbiom shift. The equations used are from [IPCC](https://www.ipcc-nggip.iges.or.jp/public/2019rf/pdf/4_Volume4/19R_V4_Ch10_Livestock.pdf).

First, I calculate only a reduction in Ym without any interaction with energy intake. This is quite simple due to the linear relationship between emissions and Ym.

Second, we assume that the missing energy usage for methane production converts fully into for carbohydrates tha the cattle can digest. Here is a non-linear relation. In the IPCC Equations, you have to adjust DE with $DE_{org}\ *\ Ym\ *\ reduction $.

Another calculation later on, could check, how large a change in DE would match a change in Ym. . In doing so, I assume that the share of reared animals in the **dairy cows** and **non-dairy cows** groups is small, so we can ignore it. This lets us find the general NE from the original GE, which lets me calculate a new GE using an adjusted DE to further adjust the methane emissions, if we assume the NE is a constant.

# Calculation for emission

In the script Function_Analyses_methane_reduction_simple.r the used function is written down. For cattle the values are summed from the subcategories, because of the non-linear link. I calculate it for the following reduction scenarios:

```{r Vec, message=FALSE, results='hide'}

red_sce <- seq(0.1, 0.5, 0.1)

```

The CRT emission data is the original value from the reported table. I calculated it new, because of rounding mistakes that would lead to Ym emission values that are not linear linked to the "original" Data without microbiome change.

## DEU

```{r DEU, message=FALSE}
CH4_emis_DE_YM_DEU_1990_2024 <- map_dfr(.x = red_sce, 
                                        CH4_emission_Ym_DE_function,
                                        CC = "DEU",
                                        YE = "2024")

write.csv(CH4_emis_DE_YM_DEU_1990_2024, 
          file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_DEU_1990_2024.csv"),
          row.names = FALSE)

#CH4_emis_DE_YM_DEU_1990_2024_1 <- read.csv(
 # file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_DEU_1990_2024.csv")
  #) -> überprüft ob gleich sind


#summary(CH4_emis_DE_YM_DEU_1990_2024)

View(CH4_emis_DE_YM_DEU_1990_2024)

```
# NZL

```{r NZL, message=FALSE}
CH4_emis_DE_YM_NZL_1990_2024 <- map_dfr(.x = red_sce, 
                                        CH4_emission_Ym_DE_function,
                                        CC = "NZL",
                                        YE = "2024")

write.csv(CH4_emis_DE_YM_NZL_1990_2024, 
          file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_NZL_1990_2024.csv"),
          row.names = FALSE)

#summary(CH4_emis_DE_YM_NZL_1990_2024)

glimpse(CH4_emis_DE_YM_NZL_1990_2024)
```
# USA

```{r USA, message=FALSE}
CH4_emis_DE_YM_USA_1990_2022 <- map_dfr(.x = red_sce, 
                                        CH4_emission_Ym_DE_function,
                                        CC = "USA",
                                        YE = "2022")

write.csv(CH4_emis_DE_YM_USA_1990_2022, 
          file = here("03_Analyses/tables/Ym_and_DE_change_simple", "CH4_emis_DE_Ym_USA_1990_2022.csv"),
          row.names = FALSE)

#summary(CH4_emis_DE_YM_USA_1990_2022)

glimpse(CH4_emis_DE_YM_USA_1990_2022)

```

