---
title: "Emission_Sectors_CH4_import"
author: "Linus Benetz"
date: "2026-07-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r General, message=FALSE, results='hide'}
rm(list = ls())

library("rio")
library("here")
library("readxl")
library("tidyr")
library("dplyr")
library("ggplot2")
library("viridis")
library("janitor")
library("purrr") # für map Befehl
library("tidyverse")
library("ggpmisc")
library("patchwork")
library("scales")

source(here::here("02_processed/code", "Function_Emis_Sectors_CH4.r"))

here()
```

# Import of main Sectors

Import from CRT-Sheet table s3. First only import for CH4 Emission from general sector. The data is for creating a time series and extrapolation for further investigation.

I use the function from **Function_Emis_Sectors_CH4.r**.

For the US there is no dtaa available for the years 2023 and 2024.

### Germany - DEU

```{r DEU1, message=FALSE, results='hide', warning=FALSE}

CH4_all_Emis_SECTORS_DEU_90_24 <- Import_total_CH4_Emis_SECTORS_function( CC = "DEU", YE = "2024")

export(CH4_all_Emis_SECTORS_DEU_90_24, 
       file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_DEU_90_24.csv"))

```
### New Zeeland - NZL

```{r NZL1, message=FALSE, results='hide', warning=FALSE}

CH4_all_Emis_SECTORS_NZL_90_24 <- Import_total_CH4_Emis_SECTORS_function( CC = "NZL", YE = "2024")

export(CH4_all_Emis_SECTORS_NZL_90_24, 
       file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_NZL_90_24.csv"))

```

### USA - USA

```{r USA1, message=FALSE, results='hide', warning=FALSE}

CH4_all_Emis_SECTORS_USA_90_22 <- Import_total_CH4_Emis_SECTORS_function( CC = "USA", YE = "2022")

export(CH4_all_Emis_SECTORS_USA_90_22, 
       file = here("02_processed/Sector_Emis_data", "CH4_all_Emis_Sectors_USA_90_22.csv"))

```
# Import of Change from 1990 to 2022

Here I will just extract the column for the change. I will take the Year 2022 because its the last year with data for the US and I want to compare the countrys. 

```{r One-CC, message=FALSE, warning=FALSE, results='hide'}
CH4_CHANGE_Emis_Sectors_all_CC_90_22 <- map_dfr(.x = c("DEU", "NZL", "USA"),
                                                .f = Import_CHANGE_CH4_Emis_SECTORS_one_CC_function,
                                                YE = 2022)

glimpse(CH4_CHANGE_Emis_Sectors_all_CC_90_22)

export(CH4_CHANGE_Emis_Sectors_all_CC_90_22,
       file = here("02_processed/Sector_Emis_data", "CH4_CHANGE_Emis_Sectors_all_CC_90_22.csv"))

```


# Import of Subcategories for Agriculture Sector

For further investigation and extrapolation I want to change the value for Agricultre with adjustment of *enteric fermentation*. So I download the data for Agriculture with the subcategories separately.

### Germany - DEU

```{r DEU2, message=FALSE, results='hide', warning=FALSE}

CH4__Emis_SECTOR_Agriculture_DEU_90_24 <- Import_CH4_Emis_SECTOR_AGRICULTURE_function( CC = "DEU", YE = "2024")

export(CH4__Emis_SECTOR_Agriculture_DEU_90_24, 
       file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_DEU_90_24.csv"))

```
### New Zeeland - NZL

```{r NZL2, message=FALSE, results='hide', warning=FALSE}

CH4_Emis_SECTOR_Agriculture_NZL_90_24 <- Import_CH4_Emis_SECTOR_AGRICULTURE_function( CC = "NZL", YE = "2024")

export(CH4_Emis_SECTOR_Agriculture_NZL_90_24, 
       file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_NZL_90_24.csv"))

```

### USA - USA

```{r USA2, message=FALSE, results='hide', warning=FALSE}

CH4_Emis_SECTOR_AGRICULTURE_USA_90_22 <- Import_CH4_Emis_SECTOR_AGRICULTURE_function( CC = "USA", YE = "2022")

export(CH4_Emis_SECTOR_AGRICULTURE_USA_90_22, 
       file = here("02_processed/Sector_Emis_data", "CH4_Emis_Sector_AGRICULTURE_USA_90_22.csv"))

```


# Import of Share

In addition to the absolute CHnage from 90-22 I will calculate the changing Share of Agriculture and enteric fermentation for the total $CH_4$ emission, plus the shhare of enteric fermenation of the agriculture sector.

### Germany - DEU
```{r DEU_SHARE, message=FALSE, warning=FALSE}
CH4__Share_Agriculture_EntFer_DEU_90_24 <- Share_Emis_Agric_EntFer_function( CC = "DEU", YE = "2024")

export(CH4__Share_Agriculture_EntFer_DEU_90_24, 
       file = here("02_processed/Sector_Emis_data/Share_Agric_EnterFer", "CH4_SHARE_Agr_EntFer_DEU_90_24.csv"))

```

### New Zeeland - NZL
```{r NZL_SHARE, message=FALSE, warning=FALSE}
CH4__Share_Agriculture_EntFer_NZL_90_24 <- Share_Emis_Agric_EntFer_function( CC = "NZL", YE = "2024")

export(CH4__Share_Agriculture_EntFer_NZL_90_24, 
       file = here("02_processed/Sector_Emis_data/Share_Agric_EnterFer", "CH4_SHARE_Agr_EntFer_NZL_90_24.csv"))

```

### USA - USA
```{r USA_SHARE, message=FALSE, warning=FALSE}
CH4__Share_Agriculture_EntFer_USA_90_22 <- Share_Emis_Agric_EntFer_function( CC = "USA", YE = "2022")

export(CH4__Share_Agriculture_EntFer_USA_90_22, 
       file = here("02_processed/Sector_Emis_data/Share_Agric_EnterFer", "CH4_SHARE_Agr_EntFer_USA_90_22.csv"))

```

